Name matching through deep learning

### 2018-12-17 old/paper2018/evaluation.tex

 We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.  As can be seen from Table \ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 82\%.  For companies, it is from 16\% to 76\%.  Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.  For precision, the fraction of true matches found before the first error improves from 16\% to 61\% for people and 16\% to 67\% for companies.  Precision@1 improves from 10\% to 82\% for people and from 26\% to 76\% for companies.  In both these cases, demonstrable training occurred.

>>>>

 We also assessed our learning mechanism more directly by examining how the nearest neighborhood changed from before to after training.  As can be seen from Figure\ref{precision_recall}, recall is improved greatly, with the bigger change for people, in which case it improves from 3\% to 82\%.  For companies, it is from 16\% to 76\%.  Thus training is clearly effective in moving actual names for the same entity into the nearest neighbors.  For precision, the fraction of true matches found before the first error improves from 16\% to 61\% for people and 16\% to 67\% for companies.  Precision@1 improves from 10\% to 82\% for people and from 26\% to 76\% for companies.  In both these cases, demonstrable training occurred.

### 2018-12-17 old/paper2018/introduction.tex

Merging datasets is a key operation for data analytics.  A frequent
requirement for merging is joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams},
\textit{Adams, Douglas} or \textit{Douglas Noel Adams}).  Similarly,
ontology alignment can require recognizing distinct surface forms of
the same entity, especially when ontologies are independently
developed.  This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.  Data management systems have however, largely focussed solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.

@@

In this paper, we propose a novel approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.  Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.  Because a deep learning model can learn the features necessary for matching from the data, it should in theory be able to generalize better to new datasets than the data driven approaches outlined in \cite{He:2015:SJS:2824032.2824036}.   Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.  The advantage of building such a function compared to work described in \cite{auto-join-joining-tables-leveraging-transformations} is that (a) we can use this function in novel ways to completely eliminate the blocking step that is typically needed to identify the set of potentially joinable rows, as we describe below, and (b) we can use this function on arbitrary surface forms such as faces, where valid transformations of a face cannot be readily described in terms of a program.

>>>>

Merging datasets freuently requires joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams},
\textit{Adams, Douglas}).  Similarly,
ontology alignment often requires mapping different surface forms of
the same entity, especially when ontologies are independently
developed.  This problem occurs for many entity types such as people's names, company names, addresses, product descriptions, conference venues, or even people's faces.  Data management systems have however, largely focused solely on equi-joins, where string or numeric equality determines which rows should be joined, because such joins are efficient.

@@

In this paper, we propose a novel approach to the problem of joining different surface representations of the same entity, inspired in part by recent advances in deep learning.  Our approach relies on building supervised deep learning models to automatically learn the correct set of transformations needed to compute the equality of two cell values.  Conceptually, our approach is similar in spirit to the approach described in \cite{auto-join-joining-tables-leveraging-transformations}, but we use deep neural networks to learn the right function for the join operation instead of synthesizing different programs for different entity types.  The advantage of building such a function compared to work described in \cite{auto-join-joining-tables-leveraging-transformations} is that (a) we can use this function in novel ways to completely eliminate the blocking step that is typically needed to identify the set of potentially joinable rows, as we describe below, and (b) we can use this function on arbitrary surface forms such as faces, where valid transformations of a face cannot be readily described in terms of a program.

### 2018-12-17 old/paper2018/samplepaper.tex

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Merging datasets frequently requires joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams} or
\textit{Adams, Douglas}).  However, data management systems are currently limited
to performing merges based on string equality, or at best using
string similarity.  We propose an approach to name matching based on deep learning models.  
Our approach depends on (a) creating
a deep learning model that maps alternate forms for the same entity into vector space such that alternate forms are closest, (b) indexing these vectors using a nearest
neighbors algorithm to find the forms that can be potentially joined
together.  To build these models, we adapted techniques from
metric learning to the characteristics of the data; specifically we describe 
novel sample selection techniques and loss functions that work for this problem.  
To evaluate our approach, we used Wikidata as ground truth
and built models from datasets with approximately 1.1M people's names
(200K identities) and 130K company names (70K identities).  We developed models that 
allow for joins with precision@1 of .75-.81 and
recall of .74-.81.  We make the models available for aligning people or companies across multiple datasets.

>>>>

%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Merging datasets frequently requires joining across columns that have
different surface forms for the same entity (e.g., the name of a
person might be represented as \textit{Douglas Adams} or
\textit{Adams, Douglas}).  However, data management systems are currently limited
to performing merges based on string equality, or at best using
string similarity.  We propose an approach to name matching based on deep learning models.  
Our approach depends on (a) creating
a deep learning model that maps alternate forms for the same entity into vector space such that alternate forms are closest, (b) indexing these vectors using a nearest
neighbors algorithm to find the forms that can be potentially joined
together.  To build these models, we adapted techniques from
metric learning to the characteristics of the data; specifically we describe 
novel sample selection techniques and loss functions that work for this problem.  
To evaluate our approach, we used Wikidata as ground truth
and built models from datasets with approximately 1.1M people's names
(200K identities) and 130K company names (70K identities).  We developed models that 
allow for joins with precision@1 of .76-.82 and
recall of .74-.79.  We make the models available for aligning people or company names across multiple datasets.
